---
title: "visualization_and_EDA"
subtitle: "part_1"
output: github_document
---

```{r}
library(tidyverse)
library(ggridges)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```

## Scatterplots

Create my first scatterplot ever
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```

New approach, same plot
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Save and edit a plot object

```{r}
weather_plot =
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced scatterplot...

STart with the same one and make it fancy!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point() + 
  geom_smooth(se = FALSE)
```

what abt the 'aes' placement?

```{r}
weather_df %>%  
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```

Let's facet some things
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.05) +
  geom_smooth(se = FALSE, size = 2) +
  facet_grid(. ~ name)
```

Let's combine some elements and try a new plot.
```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(alpha = 0.05) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~name)
```

## Some small notes

How nmany goems haven to exist?

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

You can use a neat geom

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density2d() +
  geom_point(alpha = .3)
```

## Univariate plots

histograms
```{r}
weather_df %>% 
  ggplot(aes(x=tmin)) +
  geom_histogram()
```

```{r}
weather_df %>% 
  ggplot(aes(x=tmin, fill = name)) +
  geom_histogram() +
  facet_grid(. ~ name)
```

Let's try a new geometry.

```{r}
weather_df %>% 
  ggplot(aes(x=tmin, fill = name)) +
  geom_density(alpha = 0.3)
```

What abt box plots?

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot()

```
Trendy plots
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = .5) +
  stat_summary()
```

Ridge plots - most popular plot of 2017

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```

## save and embed

Save a scatterplot
```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5)

```

Embed at different size
```{r, fig.width=12, fig.height=8}
weather_plot

```

